---
title: "RegressionProject"
author: "Hnin Su PHYU"
date: "8/27/2020"
output: pdf_document
---

##Overview
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"
##Dataset
```{r}
library(datasets)
data(mtcars)
head(mtcars)
```
##Processing Data
```{r}
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
str(mtcars)
```
##Exploratory analysis with Appendix: Figures
The mean of the variant cars (by transmission types) for their MPG:
```{r}
mtcars$am<-as.factor(mtcars$am)
levels(mtcars$am)<-c("Auto", "Man.")
aggregate(mpg ~ am, data = mtcars, mean)
```
We can see from this simple view that the mean average of MPG’s for Automatic cars outstrips that of Manual.

We should see if this variance is significant - via running a t-test:
```{r}
Auto.Data <- mtcars[mtcars$am == "Auto",]
Manu.Data <- mtcars[mtcars$am == "Man.",]

t.test(Auto.Data$mpg, Manu.Data$mpg)
```
```{r}
library(ggplot2)
## Box Plot  of MPG by Transmission Type
g <- ggplot(aes(x = am, y = mpg), data = mtcars)  
g <- g + geom_boxplot(aes(fill = am))
g + labs(x = "Transmission Type", y = "MPG", title = "MPG by Transmission Type") +
        theme(plot.title = element_text(color="grey25", face="bold",hjust=0.5)) +
        scale_fill_manual(values=c("aquamarine4","lightsteelblue4"))
```
```{r}
## Histgram of MPG
hist(mtcars$mpg, breaks=12, xlab="Miles Per Gallon (MPG)", main="MPG Distribution", col="aquamarine4")
```
##Regression modelling
```{r}
singleVariableRegressionModel <- lm(mpg ~ am, data = mtcars)
summary(singleVariableRegressionModel)
```

Since Adjusted R^2 = 0.3385, thus only 33.85% of the regression variance of this model is explained.

```{r}
multiVariableRegressionModel <- lm(mpg ~ am + wt + hp, data = mtcars)
summary(multiVariableRegressionModel)
```
Compared to single variable regression model, the Adjusted R^2 = 0.823, thus approximately 82.3% of the regression variance of this model is explained.
```{r}
anova(singleVariableRegressionModel, multiVariableRegressionModel)
```
Since the p-value is 3.745e-09, we can now reject the H0 and state that our Multivariable Model is considerably different than the Single Linear Regression Model.
```{r}
t.test(mtcars$mpg~mtcars$am)
```
With assumption that all other conditions remain unchanged. Since p-value = 0.001374 which is less than 0.05, we conclude that manual transmission is better than automatic transmission for MPG and reject the null hypothesis that there is no difference in MPG.

##Executive Summary
The key finding of this analysis is that manual transmission on average has a better miles per gallon (mpg) than its counterpart i.e. automatic transmission.



























